MCLM parameters, interactive example

### 2024-05-20 apps/Graphical_representation_interactive.qmd
Renders item in original coordinates

output$ts_original <- renderPlot({
})

>>>>

# Render item in original coordinates:
output$ts_original <- renderPlot({

  item_oblique() |>
    ggplot(
      aes(
        origin_1, origin_2,
        xend  = end_1, yend = end_2,
        color = I("red"), fill = I("red")
      ),
    )                                                  +
    geom_vline(xintercept = 0, linewidth = LINE_WIDTH) +
    geom_hline(yintercept = 0, linewidth = LINE_WIDTH) +
    geom_segment(
      arrow     = arrow(
        angle  = 20,
        length = unit(10, "points"),
        type   = "closed"
      ),
      linejoin  = "mitre",
      linewidth = VECTOR_WIDTH
    ) +
    scale_x_continuous(
      limits       = LIMITS,
      breaks       = BREAKS,
      minor_breaks = NULL,
      name         = NULL,
      oob          = oob_keep
    ) +
    scale_y_continuous(
      limits       = LIMITS,
      breaks       = BREAKS,
      name         = NULL,
      oob          = oob_keep
    ) +
    coord_fixed(expand = FALSE, clip = "on") +
    theme(
      axis.line        = element_blank(),
      panel.grid.major = element_line(
        color     = "black",
        linewidth = LINE_WIDTH,
        linetype  = "C6"
      )
    )
})
